Flabby and injective objects in toposes

### 2022-02-14 paper-flabby-objects.tex
typo

\begin{proof}Let~$M$ be a module. First we'll assume that~$M$
is a sheaf for some modal operator~$\nabla$ such that for any
formula~$\varphi$, $\nabla(\varphi \vee (\varphi \Rightarrow \nabla\bot))$. In
this case, the module~$M$ is already functionally flabby: A witnessing choice
function maps a subsingleton~$K \subseteq M$ to the unique element~$x \in M$
such that~$\nabla(x \in K')$, where~$K' \defeq K \cup \{ 0 \,|\, \text{$K$
inhabited} \Rightarrow \nabla\bot \}$. Since~$K'$ has the property
that~$\nabla(\text{$K$ is a singleton})$, such an element~$x$ exists and is unique
by the sheaf condition.

>>>>

\begin{proof}Let~$M$ be a module. First we'll assume that~$M$
is a sheaf for some modal operator~$\nabla$ such that for any
formula~$\varphi$, $\nabla(\varphi \vee (\varphi \Rightarrow \nabla\bot))$. In
this case, the module~$M$ is already functionally flabby: A witnessing choice
function maps a subterminal~$K \subseteq M$ to the unique element~$x \in M$
such that~$\nabla(x \in K')$, where~$K' \defeq K \cup \{ 0 \,|\, \text{$K$
inhabited} \Rightarrow \nabla\bot \}$. Since~$K'$ has the property
that~$\nabla(\text{$K$ is a singleton})$, such an element~$x$ exists and is unique
by the sheaf condition.
